LLM-based agents increasingly rely on external memory systems to maintain information across long-term interactions. However, real-world memories are often not static facts: user preferences, plans, task progress, and event descriptions may evolve through multiple semantic states. Existing benchmarks have advanced the evaluation of long-term memory, temporal reasoning, and knowledge update, but they rarely isolate whether the stage-correct state can be retrieved from a memory system given an evolving memory trajectory. To address this gap, we introduce \textbf{TSSMRBench}, a benchmark for temporal semantic state memory retrieval.

TSSMRBench formalizes this problem as retrieval over evolving state trajectories and asks whether an agent's memory system can recover the state evidence required by a query rather than merely a relevant or recent memory. We construct a benchmark with 300 scenarios, 9{,}000 memory nodes, and 900 multiple-choice questions organized into three task families: \emph{single-state lookup}, \emph{cross-version comparison}, and \emph{temporal ordering}. The tasks differ in how many supporting states they require, enabling evaluation of both retrieval precision and support completeness under shared-pool interference.

Experiments with BM25, FAISS, Mem0, and Graphiti show that current retrieval baselines and memory systems perform relatively well on single-state queries but degrade substantially on cross-version comparison and temporal-ordering queries. Dense retrieval remains the strongest simple baseline, while memory systems expose trade-offs between granularity, support recovery, and latency. These findings show that temporal semantic state retrieval remains challenging for current agent memory systems and suggest that future designs should preserve version history, retrieve coherent state-level evidence, and support stage-aware selection among semantically similar memories.
